Transforming Trash as an Artistic Act

### 2015-12-06 main.tex
re organization
Former-commit-id: f7f7ca407330448c19799f535ba2ea18fbe043ee
Reorganization
Former-commit-id: d2f4ba3d6ef984f2a64e4a3f955bf472f7cb7cc7
Reduction
Former-commit-id: c287ed58ed0af64082641437043495694a05ba72
Reduction
Former-commit-id: 5f9534d56a5913adc6ea4ef6840a4bdae4860f35
Reduction
Former-commit-id: 776addea2a8d261fe4b62f86718a2555ef817347
reduction
Former-commit-id: c9bcc8bcd3f9852bbc75b9d9620cfb397ada7b06
reduction
Former-commit-id: 6bbc0d2d54fc40b36523e0d0976e845eec1e8bf2

\documentclass[12pt]{report}
\usepackage[hidelinks]{hyperref}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[turkish,english,shorthands=:!]{babel}
\usepackage{apacite}
\usepackage[a4paper,width=155mm,top=25mm,bottom=25mm]{geometry}
\usepackage{epigraph}
\usepackage{graphicx}
%\graphicspath{ {graphics/} }
\usepackage{float}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{wrapfig}
\usepackage[usenames, dvipsnames]{color}
\usepackage[titletoc]{appendix}
\usepackage[colorinlistoftodos]{todonotes}

@@

\providecommand{\quotes}[1]{``#1''}
\providecommand{\singlequotes}[1]{`#1'}
%\providecommand{\todo}[1]{\textcolor{red}{#1}}
\providecommand{\comment}[1]{\textcolor{cyan}{#1}}
\providecommand{\paraphrase}[1]{\textcolor{magenta}{#1}}

\newenvironment{blockquote}{%
  \par%
  \medskip
  \leftskip=4em\rightskip=2em%
  \noindent\ignorespaces}{%
  \par\medskip}

\renewcommand*\bibname{Bibliography}

@@

%****************************************
% Ideas for Abstract
% You can add short definition of trash. Any object can be art in 20th century. Society generated trash and a culture that do not reuse and throws away.
% Structure of this thesis: written part of it and the project support each other.
%........................................

%****************************************
% Structure of Abstract
% What is this study?
% What is questioned/examined/investigated?
% How is it investigated?
% What is the outcome?
%........................................

%****************************************
% ENGLISH
\begin{abstract}
The purpose of this study is to discuss transformation of trash in the context of (art and) artistic act. Approach and methodologies of artists who uses discarded materials in their works are explored. It is questioned that why and how they use discarded materials. How can artworks be understood in terms of theoretical and cultural aspects?

\comment{The purpose of this thesis is to explore the transformation of discarded items through the artistic methodologies (or in the context of art). It is questioned that the role of art in transformation of discarded items. This thesis follows the discussions of what is waste and the states of waste or meaning of waste. Within this thesis the project transformed the collected discarded items and then later spreads them to the community again.}

Artists has used trash to reproduce artwork since the first ready-made introduced. \comment{first examples are not actually made of trash. not considered as trash, but entering non-art object traced back to beginning of 20th century.}

\comment{First ready-made (or using non-art) object in the art making has extended the language of art and opened new playground for artist.}

Within this framework, thesis project argues that it is possible to see the process of collecting, transforming and placing trash as an artistic act. Notebooks are made from trash/discarded papers by the help of people. Process and notebooks are recorded on a website. Notebooks are distributed in different locations.

%\todo[inline]{Does trash can be seen as a (new) resource for artist.}

\vfill\noindent\textbf{Keywords:} Transformation of Trash, Trash in Art, Rubbish Theory?, Throw Away Culture?, Handmade Notebooks.
\end{abstract}
%........................................

@@

%****************************************
% SAMPLE ABSTRACTS

% Bu çalışmada, ne kadar itici bir kavram olsa da, çöplük olgusunun çirkinlikten güzelliğe ulaşarak estetik bir haz uyandırması amaç edinilmiştir. Iticici gözüken bir konunun resim diliyle anlatımı ile tersine çekici ilginç bir sanat konusu olabileceğinin somutlaştırılması amaçlanmıştır. Sanatçı bir anlamda doğada yaşamda bulunan küçük ayrıntıları, sanatsal bir gözle yaklaşarak gösterebilendir. Resim için konu denince hep bildik tanıdık nesneler, belli bir düzenleme anlayışı (Natürmort) ya da idealize edilmiş konular, temalar akla gelir. Oysa önemsiz gibi gözüken itici karmaşık konular bile sanatsal kaygılarla ele ahnabilmelidir. Önemli olan, bu konalara estetik yaklaşım ve izlenen anlatım yol ve teknikleridir. Özgün baskı dallarından kazı resim (gravür) tekniğinin ele alınan konunun görselleştirilmesinde, anlatımında en uygun teknik olmasıdır. Çünkü her sanatçı kendi doğasına en uygun olan teknik ve malzemelerin olanaklarıyla kendini en rahat biçimde ifade etme olanağı bulur. Kendine özgü bir biçim ve anlatım diliyle dile getirmek gerçekleştirmek çabalan özgünlüğü yakalamak içindir. Bu çalışmada özgünlüğü yakalamak, çöplük olgusunun oluşturduğu dinamik yapı, objelerin biçimlerine bağlı kalmadan plastik dille görselleştirilmiştir. Seçilen teknik doğası gereği raslantısal tadlarada olanak vermektedir. Oluşturulan resimlerde durağan bir dengeden çok dinamik biçim ilişkilerine dayanan gerilimli bir etkinin yakalanması amaçlanmıştır.

% ON THE RELATIONSHIP BETWEEN IMAGES AND WORDS AND THEIR RELATION TO BODY AND PERCEPTION
% Prehistoric man created a mark and throughout the history this mark evolved and bifurcated into two: a word and an image. While images were cherished, words were set apart from images. 
% This thesis attempts to look at the relationship between images and words through seeking their connection to perception and body. It investigates how image-word dichotomy occurred and how this dichotomy obscured the connection between writing and body. The thesis also examines different approaches to overcome this phenomenon in the context of Modern Art. 
% By examining my artwork within this framework, it argues that it is possible to embody the inseparable relationship between images and words through reconnecting with the body’s primordial existence.

% ALTERNATIVE PHOTOGRAPHY IN THE DIGITAL AGE: PERFECT PHOTOGRAPHS IN AN IMPERFECT WAY
% This thesis explores the possibility of an alternative future of photography from the union of digital and chemical domains of the photographic medium. The historical photographic processes known as Cyanotype, Salt print and Vandyke Brown are employed for this project in conjunction with the modern inkjet printer produced digital negatives. 
% As being highly sensitive to the variables during the process, each alternative photographic print exhibits a visual uniqueness. In this aspect, there is conceptual correlation with the visual uniqueness of alternative photographic processes and the visual uniqueness of albinism. Emphasizing the human element in subject, vision and craft of making photographs, this project aims to produce unique photographs of a visually unique subject.

% LAND ART ON THE BORDER BETWEEN TOPOLOGY AND ATOPOLOGY
% The purpose of this study is to discuss the Land Art movement from a topological and atopological perspective. In order to establish an extensive understanding of the matters of topology and atopology, Arkady Plotnitsky’s formalization of quasi- mathematical thinking, which is derived from Jacques Derrida’s philosophy, is treated in detail. The artistic stance, Robert Smithson, as a major figure of Land Art movement is analyzed both from the artistic and the theoretical perspectives. Thereafter, an algebraic reading of the Smithsonian conceptualization is executed in order to illuminate the liaison between the Land Art movement and the matters of topology and atopology. Finally, the thesis project, Nonlocalizable Displaced Mirrors depicts the whole attitude, which is taken throughout the study, towards the issue of Land Art on the Border between Topology and Atopology.

%........................................

@@

\pagenumbering{arabic}
\include{chapter1}
\include{chapter2}
\include{chapter3}
\include{chapter4}
\include{chapter5}
\include{uncategorized}
\bibliographystyle{apacite}
\bibliography{literature}
\begin{appendices}
\include{appendix_glossary}
\end{appendices}

>>>>

\documentclass[12pt]{report}
\usepackage[hidelinks]{hyperref}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[turkish,english,shorthands=:!]{babel}
\usepackage{apacite}
\usepackage[a4paper,width=155mm,top=25mm,bottom=25mm]{geometry}
\usepackage{epigraph}
\usepackage{graphicx}
%\graphicspath{ {graphics/} }
\usepackage{float}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{wrapfig}
\usepackage[usenames,dvipsnames]{color}
\usepackage[titletoc]{appendix}
\usepackage[colorinlistoftodos]{todonotes}

@@

\providecommand{\quotes}[1]{``#1''}
\providecommand{\singlequotes}[1]{`#1'}
\providecommand{\comment}[1]{\textcolor{cyan}{#1}}
\providecommand{\summary}[1]{\textcolor{green}{[#1]}}
\providecommand{\paraphrase}[1]{\textcolor{magenta}{\quotes{#1}}}
\renewcommand*\bibname{Bibliography}

@@

%****************************************
% ENGLISH
\begin{abstract}
Usage of non-art objects in the artworks can be traced back to the beginning of 20th century. This approach has broken the existing rules and extended the language of art in an unprecedented way. After that point, trash has found a place in the work of artists \comment{(and their expression)}.

The purpose of this study is to discuss transformation (or usage) of trash in the context of (art and) artistic act. It is questioned that the role of art in the transformation of discarded items. Approaches and methodologies of artists who use discarded materials in their works are explored. This thesis follows the discussions of the place of trash in culture and theories of trash. Then approaches and methodologies of artists who use discarded materials in their works are explored. \comment{Usage of discarded materials in the artwork by the contemporary artist are studied through their works.} It is questioned that why and how they use discarded materials and how artworks can be understood regarding theoretical and cultural aspects.

Within this framework, thesis project argues that it is possible to see the process of collecting, transforming and placing trash as an artistic act. In the scope of the project, discarded papers are collected with the help people and transformed to notebooks. Progress and collected items are recorded on a website. Notebooks are installed in different locations in order to invite people to use trash again.

\vfill\noindent\textbf{Keywords:} Transformation of Trash, Trash in Art, Trash as an Art Material.
\end{abstract}
%........................................

@@

@@

\pagenumbering{arabic}
\include{chapter1_reduced}
\include{chapter2_reduced}
\include{chapter3_reduced}
\include{chapter4_reduced}
\include{chapter5}
\bibliographystyle{apacite}
\bibliography{literature}
\begin{appendices}
\include{appendix_glossary}
\end{appendices}
